For length-based models the length structure of the partition has \(n_l\) length bins where \(l_i\) denotes length bin \(i\) with minimum length value denoted by \(lc_i\) and midpoint denoted as \(lm_i\).
\[lm_i = 0.5 \left(lc_i + lc_{i+1}\right)\]

In length-based models a growth transition matrix describes the probability of fish moving from length bin \(l_j\) to length bin \(l_k\). The growth increment models describe the expected mean length increment denoted by \(\mu_i\) for fish in length bin \(l_i\).

Note that the presence of a model plus-group will affect the behaviour of the growth transition matrix. 

In models with a length plus group (i.e., \commandsubarg{model}{length\_plus}{true}) then every individual is 'grown' according to the growth transition matrix (i.e., individuals in each length bin are redistributed to, typically larger, length bins). Individuals where the growth increment would result in a size larger then the plus group size are assumed to become that size, and no individuals are 'lost'. 

In models without a length plus group (i.e., \commandsubarg{model}{length\_plus}{false}), some individuals may have a growth increment that would result in them being larger than the largest length bin in the model. In this case, these individuals 'fall off the end' and are 'lost' to the mode, i.e., the are removed from the model. This approximates a similar process in age-based models with the ageing process and the presence or absence of a model age plus group. 

\subsubsection{The `none' model}\index{Growth Increment!None}\label{sec:GrowthIncrement-None}

All individuals have a mean length increment of 1 regardless of where they are in the length partition.

\subsubsection{The exponential model}\index{Growth Increment!Exponential}\label{sec:GrowthIncrement-Exponential}

\begin{equation}
\mu_i = g_\alpha \left(\frac{g_\beta}{g_\alpha} \right)^{\frac{(lm_i - l_\alpha)}{(l_\beta - l_\alpha)}}
\end{equation}

\subsubsection{The basic model}\index{Growth Increment!Basic}\label{sec:GrowthIncrement-Basic}

\begin{equation}
\mu_i = g_\alpha + (g_\beta - g_\alpha) \frac{lm_i - l_\alpha}{l_\beta - l_\alpha}
\end{equation}

%
%\subsubsection{The Schnute model}\index{Schnute Increment!Exponential}\label{sec:GrowthIncrement-Schnute}
%This is derived from \cite{haist2009multi} and doesn't look to be working as expected. It has estimable parameter \(g_{diff}\), \(g_{\alpha}\) and \(\gamma\). The generalised Schnute model applies grows individuals from time-step \(t\) to time-step \(t+1\) as
%
%\begin{equation}
%l_{t+1} = \left(l_t \exp(-\kappa\Delta t) + \zeta^{\gamma} \left(1 - \exp(-\kappa\Delta t)\right)\right)^{1/\gamma}
%\end{equation}
%%
%where, \(\Delta t\) is the proportion of annual growth between time-steps and other derived parameters are described below. The expected increment becomes
%\[
%\mu_{t} | l_t = l_{t+1} - l_t
%\]
%\begin{align*}
%	\kappa &= -\log\left(1 - \frac{a - b}{l_{\alpha}^{\gamma} - l_{\beta}^{\gamma}} \right)\\
%	\zeta &= \frac{l_{\alpha}^{\gamma} - l_{\alpha}^{\gamma}(b/a)}{1 - (b/a)}\\
%	a &= (l_{\alpha} + g_{\alpha})^{\gamma} - l_{\alpha}^{\gamma}\\	
%	b &= (l_{\beta} + g_{\beta})^{\gamma} - l_{\beta}^{\gamma}\\
%	g_{\beta} & = g_{diff} g_{\alpha}
%\end{align*}
%%
%here, \(l_{\alpha}\) and \(l_{\beta}\) are lengths that correspond to the parameters \(g_{\alpha}\) \(g_{\beta}\) which describe expected length increments for those reference lengths.  

\subsubsection{Growth transition matrix}\index{Growth Increment!Growth Transition Matrix}\label{sec:GrowthIncrement-GrowthMatrix}

The probability of a fish in length bin \(i\) moving into length bin \(j\) is defined by the growth transition matrix. This matrix is defined by length bin midpoints (\(lm_i\)) mean increment \(\mu_i\) a standard deviation and distribution assumption.

All growth increment models require a coefficient of variation (\(cv\)) and minimum standard deviation \(\sigma_{min}\). 

\[
\sigma_i = max(\sigma_{min}, \mu_i cv)
\]

The growth transition matrix in time step \(t\) denoted by \(\mathbf{G^t}\)is defined as follows

\begin{equation}
G^t_{i,j} = 
\begin{cases}
0.0 \ , & \text{ for } j < i \ \text{no negative growth}\\
f(lc_{i + 1},\mu_i, \sigma_i) \ , & \text{ for } i = j \\
1.0 - \sum\limits_{k = 1}^{n_l - 1}G^t_{i,k} \ , & \text{ for } i = n_l \ \& \ \text{plus group} \\
f(lc_{n_l + 1},\mu_i, \sigma_i) - \sum\limits_{k = 1}^{n_l - 1}G^t_{i,k} \ , & \text{ for } i = n_l \ \&  \  \text{no plus group} \\		
\end{cases}
\end{equation}

where, \(f(X,\mu, \sigma)\) is the cumulative density function defined by \subcommand{distribution}. Currently only the Normal distribution is allowed.
