\defComLab{likelihood}{Define an object of type \emph{Likelihood}}
\defRef{sec:Likelihood}
\label{syntax:Likelihood}

\subsubsection{Likelihood of type binomial}
\commandlabsubarg{likelihood}{type}{Binomial}
\label{syntax:Likelihood-Binomial}

The Binomial type has no additional subcommands.

\subsubsection{Likelihood of type binomial approx}
\commandlabsubarg{likelihood}{type}{Binomial\_Approx}
\label{syntax:Likelihood-BinomialApprox}

The Binomial\_Approx type has no additional subcommands.

\subsubsection{Likelihood of type Dirichlet}
\commandlabsubarg{likelihood}{type}{Dirichlet}
\label{syntax:Likelihood-Dirichlet}

The Dirichlet type has no additional subcommands.

\subsubsection{Likelihood of type Dirichlet-multinomial}
\commandlabsubarg{likelihood}{type}{Dirichlet\_Multinomial}
\label{syntax:Likelihood-Dirichlet-Multinomial}

The Dirichlet-multinomial type has no additional subcommands.

\subsubsection{Likelihood of type lognormal}
\commandlabsubarg{likelihood}{type}{Log\_Normal}
\label{syntax:Likelihood-LogNormal}

The Log\_Normal type has no additional subcommands.

\subsubsection{Likelihood of type lognormal with q}
\commandlabsubarg{likelihood}{type}{Log\_Normal\_With\_Q}
\label{syntax:Likelihood-LogNormalWithQ}

The Log\_Normal\_With\_Q type has no additional subcommands.

\subsubsection{Likelihood of type multinomial}
\commandlabsubarg{likelihood}{type}{Multinomial}
\label{syntax:Likelihood-Multinomial}

The Multinomial type has no additional subcommands.

\subsubsection{Likelihood of type normal}
\commandlabsubarg{likelihood}{type}{Normal}
\label{syntax:Likelihood-Normal}

The Normal type has no additional subcommands.

\subsubsection{Likelihood of type pseudo}
\commandlabsubarg{likelihood}{type}{none}
\label{syntax:Likelihood-Pseudo}

The Pseudo type has no additional subcommands.

\subsubsection{Likelihood of type Bernoulli}
\commandlabsubarg{likelihood}{type}{Bernoulli}
\label{syntax:Likelihood-Bernoulli}
