\section{Introduction\label{sec:Introduction}}

The Contributors Guide provides an overview for those who wish to compile the latest version of \CNAME and contribute to the \CNAME\ source code. \CNAME\ is open source and the Development Team encourages users to submit and contribute changes, bug fixes, and enhancements. This document is intended to provide a guide for those who wish to undertake these tasks. 

The \CNAME\ source code is hosted on GitHub, and can be found at \url{https://github.com/Casal2/CASAL2}.

A release bundle which includes a binary (both windows and Linux operating systems), manual, examples, \R\  package and other help guides can be downloaded at \url{https://github.com/Casal2/CASAL2/releases}. Note that the release versions on the repository can lag behind the latest source code as release versions are only compiled periodically. 

This document provides a guide to understanding how to access the source code, how to compile and build, and the guidelines for submitting code changes to the main \CNAME\ repository. It also provides a simple introduction to setting up a GitHub profile and using git. 

As a suggestion, it may be helpful to contact the Development Team before making any changes to the code. The Development Team can assist with ideas on how best to add functionality. Either contact them directly at \emaillink\ or open an issue at \url{https://github.com/Casal2/CASAL2/issues}. 

If you have any questions or require more information, please contact the \CNAME\ Development Team at \emaillink.